Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-04-10 tese2/13_implementation_model.tex
[ADD] thesis video play mechanisms

Our first decision for our model in order to avoid repeated code, was the isolation of the object's attributes from themselves, so we could apply the search operation to a set of attributes independently from the object type. To this generic set of properties we call data and each object of this type has a reference to the owner, which is a unique identification number.

\begin{table}[!htb]
\centering
\caption{Generic data model}
\label{my-label}
    \begin{tabular}{cc}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{Data}}                                \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId                         \\ 
            $\medbullet$ owner           & ObjectId                            \\ 
            $\medbullet$ properties      & List[Attribute] \\ 
            $\medcirc$ searchableValues & List[Text]        \\ \hline
        \end{tabular}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{Attribute}}                           \\ \hline
            $\medbullet$ key           & Text                                  \\ 
            $\medcirc$ value           & Object                              \\ 
            $\medbullet$ identifiable    & Boolean                             \\ 
            $\medcirc$ readPermissions &  List[ObjectId]   \\ 
            $\medcirc$ writePermissions  & List[ObjectId]  \\ \hline
        \end{tabular}    
    \end{tabular}
\end{table}

@@

The user model is not tied to the user attributes, the information maintained in this model is just used for authentication purposes. Passwords are not stored in plain text, instead we apply hashing and salting techniques \cite{password} in order to make it harder to decode the password by an attacker. Accordingly, we use \emph{SHA-1} and a random salt per user with 32 characters long.

\begin{table}[!htb]
\centering
\caption{User model}
\label{my-label}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{User}}                             \\ \hline
        $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
        $\medbullet$ hash           & Text                         \\ 
        $\medbullet$ salt      & Text                         \\ \hline
    \end{tabular}
\end{table}

@@

A relation between two entities $e_1$ and $e_2$ is represented by the pair $e_1\rightarrow e_2$, where $e_1$ is the source and $e_2$ is the target. This relation is said bi-directional if and only if it also exists the relation $e_2\rightarrow e_1$.

\begin{table}[!htb]
\centering
\caption{Relation model}
\label{my-label}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{Relation}}                             \\ \hline
        $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
        $\medbullet$ source           & ObjectId                         \\ 
        $\medbullet$ target      & ObjectId                         \\ \hline
    \end{tabular}
\end{table}

@@

A group can be public or private. If the group is public then it is visible to all users that maintain a friendship with a member of this group. If the group is private then it is only visible to their members.

\begin{table}[!htb]
\centering
\caption{Group model}
\label{my-label}
    \begin{tabular}{cc}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{Group}}                             \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
            $\medcirc$ inviteToken           & Text                         \\ 
            $\medbullet$ visibility      & Text                         \\ \hline
        \end{tabular}

@@

A message is composed by its content, sequence number, time of creation and source and target identification numbers. The message's target can reference any of object but our application is only covering messages to groups.

\begin{table}[!htb]
\centering
\caption{Message model}
\label{my-label}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{Message}}                             \\ \hline
        $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
        $\medbullet$ source           & ObjectId                         \\ 
        $\medbullet$ target      & ObjectId                         \\ 
        $\medbullet$ sequence      & Number                         \\ 
        $\medbullet$ content      & Text                         \\ \hline
    \end{tabular}
\end{table}

@@

During a conversation, users may allow sharing their web cameras, by doing so their video is stored in recording chunks. Each chunk represents an interval of time  $T=\big[c^{start},c^{end}\big[$, it contains a reference to a group and list of \ac{URL}s with the correspondent owner identification number and \emph{WebSocket} session id.

@@

\begin{table}[!htb]
\centering
    \caption{Recording model}
    \label{my-label}
    \begin{tabular}{cc}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{RecordingInterval}}                   \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
            $\medbullet$ groupId            & ObjectId                         \\ 
             $\medbullet$ start             & Date                         \\ 
            $\medbullet$ end                & Date                         \\ \hline
        \end{tabular}   
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{RecordingChunk}}                             \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
            $\medbullet$ groupId            & ObjectId                         \\ 
            $\medbullet$ interval           & ObjectId                      \\ 
            $\medbullet$ start              & Date                         \\ 
            $\medbullet$ end                & Date                         \\ 
            $\medbullet$ sequenceNumber     & Number                         \\ 
            $\medbullet$ urls               & Document                       \\ \hline
        \end{tabular}
    \end{tabular}
\end{table}

>>>>

Our first decision for our model in order to avoid repeated code, was the isolation of the object's attributes from themselves, so we could apply the search operation to a set of attributes independently from the object type. To this generic set of properties we call data (table \ref{table:generic}) and each object of this type has a reference to the owner, which is a unique identification number.

\begin{table}[!htb]
\centering
\caption{Generic data model}
\label{table:generic}
    \begin{tabular}{cc}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{Data}}                                \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId                         \\ 
            $\medbullet$ owner           & ObjectId                            \\ 
            $\medbullet$ properties      & List[Attribute] \\ 
            $\medcirc$ searchableValues & List[Text]        \\ \hline
        \end{tabular}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{Attribute}}                           \\ \hline
            $\medbullet$ key           & Text                                  \\ 
            $\medcirc$ value           & Object                              \\ 
            $\medbullet$ identifiable    & Boolean                             \\ 
            $\medcirc$ readPermissions &  List[ObjectId]   \\ 
            $\medcirc$ writePermissions  & List[ObjectId]  \\ \hline
        \end{tabular}    
    \end{tabular}
\end{table}

@@

The user model is not tied to the user attributes (table \ref{table:user}), the information maintained in this model is just used for authentication purposes. Passwords are not stored in plain text, instead we apply hashing and salting techniques \cite{password} in order to make it harder to decode the password by an attacker. Accordingly, we use \emph{SHA-1} and a random salt per user with 32 characters long.

\begin{table}[!htb]
\centering
\caption{User model}
\label{table:user}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{User}}                             \\ \hline
        $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
        $\medbullet$ hash           & Text                         \\ 
        $\medbullet$ salt      & Text                         \\ \hline
    \end{tabular}
\end{table}

@@

A relation between two entities $e_1$ and $e_2$ is represented by the pair $e_1\rightarrow e_2$ (table \ref{table:relation}), where $e_1$ is the source and $e_2$ is the target. This relation is said bi-directional if and only if it also exists the relation $e_2\rightarrow e_1$.

\begin{table}[!htb]
\centering
\caption{Relation model}
\label{table:relation}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{Relation}}                             \\ \hline
        $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
        $\medbullet$ source           & ObjectId                         \\ 
        $\medbullet$ target      & ObjectId                         \\ \hline
    \end{tabular}
\end{table}

@@

A group is composed by an \emph{id}, \emph{inviteToken} and a \emph{visibility} as shown on table \ref{table:group}.

Moreover, a group can be public or private. If the group is public then it is visible to all users that maintain a friendship with a member of this group. If the group is private then it is only visible to their members.

\begin{table}[!htb]
\centering
\caption{Group model}
\label{table:group}
    \begin{tabular}{cc}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{Group}}             \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId       \\ 
            $\medcirc$ inviteToken           & Text          \\ 
            $\medbullet$ visibility      & Text              \\ \hline
        \end{tabular}

@@

A message is composed by its content, time of creation and source and target identification numbers (table \ref{table:message}). The message's target can reference any of object but our application is only covering messages to groups.

\begin{table}[!htb]
\centering
\caption{Message model}
\label{table:message}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{Message}}                             \\ \hline
        $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
        $\medbullet$ source           & ObjectId                         \\ 
        $\medbullet$ target      & ObjectId                         \\ 
        $\medbullet$ content      & Text                         \\ \hline
    \end{tabular}
\end{table}

@@

During a conversation, users may allow sharing their web cameras, by doing so their video is stored in recording chunks. Each chunk represents an interval of time  $T=\big[c^{start},c^{end}\big[$, it contains the media \ac{URL}, a reference to a group, an owner identification number and the correspondent \emph{WebSocket} session id.

@@

\begin{table}[!htb]
\centering
    \caption{Recording model}
    \label{my-label}
    \begin{tabular}{cc}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{RecordingInterval}}                   \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
            $\medbullet$ groupId            & ObjectId                         \\ 
             $\medbullet$ start             & Date                         \\ 
            $\medbullet$ end                & Date                         \\ \hline
        \end{tabular}   
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{RecordingChunk}}                             \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
            $\medbullet$ groupId            & ObjectId                         \\ 
            $\medbullet$ owner           & ObjectId                      \\ 
            $\medbullet$ sessionId          & Text                       \\
            $\medbullet$ start              & Date                         \\ 
            $\medbullet$ end                & Date                         \\ 
            $\medbullet$ url               & Text                       \\ \hline
        \end{tabular}
    \end{tabular}
\end{table}

### 2016-04-10 tese2/16_implementation_content.tex
[ADD] thesis video play mechanisms

	\subsection{Synchronization}

@@

>>>>

	\subsection{Interactive media synchronization}

@@

\subsection{Non interactive media synchronization}
		By default each user receives the real time mixed video and audio of every users. As described on the previous section, users can switch the current view even for recorded media.

		Whenever a user changes the current viewed time, our server calculates which chunks to reproduce.

		In order to determine which chunks are going to be played we could find any chunk that matches the session id and intersects the given user time. Although this seems logical, we limit the size of the results to one and ignore the starting component of the recording chunk. As a consequence, we will obtain the recording chunk that ends after the playing time.

		The obtained chunk may or not intersect the given time, if it intersects than we immediately start playing the chunk, otherwise we know that the chunks starting time is after the playing time and we schedule the player to reproduce after a time duration given by the difference of the playing time and chunk starting time.

		In order to reduce the delay between switching parts we perform a query on the database for finding the next chunk to play while the selected media is playing. In order to find the next chunk we use the chunk that has a bigger id immediately after the playing chunk.

		In order to allow the users to watch an individual image and ear the audio of everyone, we are using two players, one for audio and another for video.

		If a user leaves a conference room, it is expected that the sequence of played blocks ends. When a block is not found for a given \emph{webSocket} session we try to find a block for the same user and if not possible we try to play a composite recorded block, lastly, if every attempt fails we wait for the next interval the contains media.
